---
title: "WildCard Results"
author: "Jeffrey M. Pisklak"
date: "`r Sys.Date()`"
output: html_document
bibliography: references.bib
csl: apa-with-abstract.csl

nocite: |
  @R
---

<!-- https://www.w3schools.com/tags/tag_details.asp -->
<style>
details > summary {
  padding: 4px;
  cursor: pointer;
  font-size: 2em;
}
</style>

```{r setup, include = FALSE}
options(pillar.print_max = Inf)

if (!require(knitr)) {
  install.packages("knitr")
}
if (!require(kableExtra)) {
  install.packages("kableExtra")
}
if (!require(tidyverse)) {
  install.packages("tidyverse")
}

library(knitr)
library(kableExtra)
library(tidyverse)

# Directory
# opts_knit$set(root.dir = dirname(getwd())) #Rendering from this .Rmd file.
opts_knit$set(root.dir = main_dir) # Rendering from Gen_Rmd_Doc

opts_chunk$set(
  echo = FALSE,
  # include = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7, fig.height = 5
)
```

```{r}
if (!file.exists("data/wc_full_data.csv")) {
  source("r-scripts/data_merge.R")
}
```

<!-- Participant Information -->
```{r child = 'markdown/subject_info.Rmd'}
```

<br>

---

<br>

<!-- Catch Trials -->
```{r child = 'markdown/catch_trials.Rmd'}
```

<br>

---

<br>

<!-- Risk Pref Trials -->
```{r child = 'markdown/risk_pref.Rmd'}
```

<br>

---

<br>

<!-- First Outcome Judgement-->
```{r child = 'markdown/fo_judge.Rmd'}
```

<br>

---

<br>

<!-- Frequency Judgement-->
```{r child = 'markdown/freq_judge.Rmd'}
```

<br>

---

<br>

# **R Citations**

`r R.version$version.string`

- nlme (`r packageVersion('nlme')`) [@nlme]
- patchwork (`r packageVersion('patchwork')`) [@patchwork]
- RColorBrewer (`r packageVersion('RColorBrewer')`) [@RColorBrewer]
- rcompanion (`r packageVersion('rcompanion')`) [@rcompanion]
- tidyverse (`r packageVersion('tidyverse')`) [@tidyverse]
- WRS2 (`r packageVersion('WRS2')`) [@WRS2]

<br>

---

<br>

# **References**





















