---
title: "WildCard Results"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
bibliography: bibTex/refs.bib
csl: bibTex/apa-with-abstract.csl
nocite: |
  @R
---

<!-- https://www.w3schools.com/tags/tag_details.asp -->
<style>
details > summary {
  padding: 4px;
  cursor: pointer;
  font-size: 1.5em;
}

h1.title{font-weight: bold; font-size: 3em}
h1{text-align: left; font-weight: bold; font-size: 2.5em}
h2{text-align: left; font-weight: normal; font-style: italic; font-size: 2em}
h3{text-align: left; font-size: 2em}
h4{text-align: left; font-size: 1.5em}
</style>

```{r setup, include = FALSE}
options(pillar.print_max = Inf)

if (!require(knitr)) {
  install.packages("knitr")
}
if (!require(kableExtra)) {
  install.packages("kableExtra")
}
if (!require(tidyverse)) {
  install.packages("tidyverse")
}

library(knitr)
library(kableExtra)
library(tidyverse)

# Directory
# opts_knit$set(root.dir = dirname(getwd())) #Rendering from this .Rmd file.
opts_knit$set(root.dir = main_dir) # Rendering from Gen_Rmd_Doc

opts_chunk$set(
  echo = FALSE,
  # include = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7, fig.height = 5
)
```

```{r}
# Generate data file if necessary
if (!file.exists("data/wc_full_data.csv")) {
  source("r-scripts/data_merge.R")
}

# Load preliminaries
source("r-scripts/prelim_code.R")
```

<br>

<!-- Contingencies -->

<details>
  <summary>
  Contingencies
  </summary>
  
<br>

<h5>Low Value Options</h5>
- Fixed: 30
- Risky: 20 or 40

<h5>High Value Options</h5>
- Fixed: 70
- Risky: 60 or 80
- WC-Extreme: 5 or 95
- WC-NonExtreme: 45 or 55

<h5>Group 1 - Extreme First</h5>
- Block 1-3: WC-Extreme
- Block 4-6: WC-NonExtreme
- Block 7: No WC or feedback

<h5>Group 2 - Extreme Last</h5>
- Block 1-3: WC-NonExtreme
- Block 4-6: WC-Extreme
- Block 7: No WC or feedback

<h5>Group 3 - No Extreme</h5>
- Block 1-3: WC-NonExtreme
- Block 4-6: WC-NonExtreme
- Block 7: No WC or feedback

<br>

  </details>


<br>

---

<br>

<!-- Participant Information -->
# **Participant Information**

```{r child = 'markdown/Rmd-scripts/subject_info.Rmd'}
```

<br>

---

<br>

<!-- Catch Trials -->
# **Catch Trials**

```{r child = 'markdown/Rmd-scripts/catch_trials.Rmd'}
```

<br>

---

<br>

<!-- Risk-Prefer Trials -->
# **Risk-Preference**

```{r child = 'markdown/Rmd-scripts/risk_pref.Rmd'}
```

<br>

---

<br>

<!-- First-Outcome Judgement -->
# **First-Outcome Judgement**

```{r child = 'markdown/Rmd-scripts/fo_recall.Rmd'}
```

<br>

---

<br>

<!-- Frequency Judgement -->
# **Frequency Judgement**

```{r child = 'markdown/Rmd-scripts/freq_judge.Rmd'}
```

<br>

---

<br>

# **R Citations**

`r R.version$version.string`

- Hmisc (`r packageVersion('Hmisc')`) [@Hmisc]
- rcompanion (`r packageVersion('rcompanion')`) [@rcompanion]
- RColorBrewer (`r packageVersion('RColorBrewer')`) [@RColorBrewer]
- patchwork (`r packageVersion('patchwork')`) [@patchwork]
- nlme (`r packageVersion('nlme')`) [@nlme]
- effsize (`r packageVersion('effsize')`) [@effsize]
- ggh4x (`r packageVersion('nlme')`) [@ggh4x]
- tidyverse (`r packageVersion('tidyverse')`) [@tidyverse]

<br>

---

<br>

# **References**





















