# **Participant Information**

<!-- Pre-catch Exclusion -->

```{r}
source('r-scripts/subj_stats.R')
```

<details>
  <summary>
  Pre-catch exclusion
  </summary>
  
N = `r N`
  
```{r}
kable(pre_catch, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

</details> 

<!-- Post-catch Exclusion -->

<details>
  <summary>
  Post-catch exclusion
  </summary>

N = `r (N - catch_n)`

```{r}
kable(post_catch, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

<br>

<h4>Condition totals:</h4>

```{r}
kable(cond_tot, "html", digits = 3) %>%
  kable_classic(full_width = T, position = "left", html_font = "Arial")
```

</details> 

<!-- Other Notes -->

<details>
  <summary>
  Notes
  </summary>

- Total number of catch trial exclusions = `r catch_n`.

- Some participants reported a program crash during the memory phase. Their data is included in the numbers above. For reference:

  - `r nrow(fo_comp)` crashed in the first-outcome judgment.
  - `r nrow(fj_comp)` crashed in the frequency judgment.

</details> 



