# **Frequency Judgement**

<details>
  <summary>
  Details and complications of frequency judgement results
  </summary>
  
It seems debatable whether the frequency judgement data should be plotted and analysed using means.  The data is almost certainly qualitative in nature.  For example, there is no reason to assume one person's judgment of 50% is the same as another person's. One person's 50% might be another's 70%. It's worth remembering **each participant is not providing a real frequency, they are giving their opinion about what the real frequency is.**

While the frequency judgement data has been plotted and analysed with means to remain consistent with the prior extreme-outcome work, there is a good argument that this data should be treated as nominal - similar to the first-outcome results (some might wonder why the two are being treated differently).  Admittedly, many (in Psychology) would probably argue this data is "sufficiently" quantitative given its wide sample space. Others might argue that it is qualitative, but ordinal (not nominal) and a Kruskal–Wallis test should be used. Do with this information what you will  

¯|_(ツ)_/¯
  
  <br>
  
  </details>

<details>
  <summary>
  Plot - Barplot of means
  </summary>
  
```{r, fig.width = 15, fig.height = 7}
source('r-scripts/freq_judge_analysis.R')
plt_fj_means
```

<br>

```{r}
kable(fj_bar_tab, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

<br>

</details>

<details>
  <summary>
  Plot - Violin plot
  </summary>
  
```{r, fig.width = 15, fig.height = 7}
plt_fj_violin
```

<br>

</details>

<details>
  <summary>
  2x3 ANOVA using linear mixed-effects models fit by maximum likelihood
  </summary>

<h3>ANOVA Table</h3>

```{r}
kable(aov_2x3[, -c(1)], 'html', digits = 3) %>%
  kable_classic(full_width = T, html_font = "Arial")
```

- base = intercept only (used as baseline and predicts overall mean ignoring other factors)
- cond_mod = effect of adding condition
- HL_mod = effect of adding context (i.e., High / Low choices)
- int_mod = interaction effect

<br>

<h3>Planned contrasts</h3>

```{r}
kable(round(pc, 3), 'html', digits = 3) %>%
  kable_classic(full_width = T, html_font = "Arial")
```

- E1_v_E2NE = *Extreme First* vs. combined effect of *Extreme Last* and *No Extreme*
- E2_v_NE = *Extreme Last* vs. *No Extreme*
- FJ_context1 = *High vs Low* (same test as row 3 in the ANOVA table)

<br>

<h3>Conclusions</h3> 

```{r}
df = aov_2x3$df[2:4] - aov_2x3$df[1:3]
chi = round(aov_2x3$L.Ratio[2:4], 2)
p = round(aov_2x3$`p-value`[2:4], 3)
R2 = round(aov_2x3$pseudo_R2[2:4], 2)
BF = format(round(aov_2x3$BF_10[2:4], 2), scientific = FALSE)

b = round(pc$Value[c(2, 3, 5, 6)], 3)
df_2 = round(pc$DF[c(2, 3, 5, 6)])
t = round(pc$`t-value`[c(2, 3, 5, 6)], 2)
p_2 = round(pc$`p-value`[c(2, 3, 5, 6)], 3)
r = round(pc$r_effect[c(2, 3, 5, 6)], 2)
```

**Main effect of of condition:**

$\chi^2 (`r df[1]`) = `r chi[1]`, p = `r p[1]`, R^2_N = `r R2[1]`, BF_{10} = `r BF[1]`$

- There is a small, but significant, main effect of condition on the frequency judgement of the risky doors. Note that the Bayes Factor suggests this isn't contributing any evidence.

<br>

**Main effect of of context (high vs low):**

$\chi^2 (`r df[2]`) = `r chi[2]`, p = `r p[2]`, R^2_N = `r R2[2]`, BF_{10} = `r BF[2]`$

- There is a main effect of context (high-value choices vs. low-value) on the frequency judgement of the risky doors. Bayes Factor results imply this is the only predictor of merit in the experiment.

<br>

**Interaction:**

$\chi^2 (`r df[3]`) = `r chi[3]`, p = `r p[3]`, R^2_N = `r R2[3]`, BF_{10} = `r BF[3]`$

- There is a small, but significant, interaction. The Bayes Factor suggests this isn't contributing any evidence.

<br>

**Planned comparisons:**

Extreme First vs. (Extreme Last & No Extreme)

$t(`r df_2[1]`) = `r t[1]`$, $p = `r p_2[1]`$, $r = `r r[1]`$

- The *Extreme First* condition is significantly different from the combination of the other two conditions. Note that the effect is small and may be of little practical value.

<br>

Extreme Last vs. No Extreme

$t(`r df_2[2]`) = `r t[2]`$, $p = `r p_2[2]`$, $r = `r r[2]`$

- The *Extreme Last* and *No Extreme* conditions do not significantly differ. 

<br>

Extreme First vs. (Extreme Last & No Extreme) | Context (i.e., High vs. Low)

$t(`r df_2[3]`) = `r t[3]`$, $p = `r p_2[3]`$, $r = `r r[3]`$

- The first planned comparison significantly differs depending on context (i.e., the Extreme First condition only differs from the other two conditions for the low-value choices). Note that the effect is small and may be of little practical value.

<br>

Extreme Last vs. No Extreme | Context (i.e., High vs. Low)

$t(`r df_2[4]`) = `r t[4]`$, $p = `r p_2[4]`$, $r = `r r[4]`$

- The second planned comparison does not significantly differ depending on context (i.e., no interaction with context).

<br>


**Note:** 

- $p = 0$ should be reported as $p < .001$

- $R^2_N$ is Nagelkerke's (also known as Cragg and Uhler's) pseudo $R^2$ [@Nagelkerke]. It isn't interpreted in exactly the same way as a $R^2$ based on ordinary least-squares regression, but it is bounded by 0 and 1 and higher values indicate a better model fit.

- Bayes Factors are reported as Inverse Bayes Factors, this means larger values
indicate greater support for the effect. Anything less than 1 should be considered as contributing no evidence. 

- If $BF_{10} > 150$, report that instead specifying the entire value.

</details>
