<!-- Plot -->

<details>
  <summary>
  Plot - Block means with 95% CIs
  </summary>
  
<br>
  
```{r, out.width = '60%'}
source('r-scripts/choice-trials/risk_pref_filter.R')
source('r-scripts/choice-trials/risk_pref_plots.R')
include_graphics(
  file.path(main_dir,"plots/choice-trials/plt_risky_blk.png")
)
```

<br>

</details> 

<details>
  <summary>
  Plot - Condition Differences with 95% CIs (Block 7)
  </summary>
  
<br>
  
```{r, out.width = '60%'}
include_graphics(
  file.path(main_dir, "plots/choice-trials/plt_risky_diff.png")
)
```

<br>

</details> 

<!-- Summary Stats -->

<details>
  <summary>
  Summary Statistics (Block 7)
  </summary>
  
<br>

```{r}
s <- risky_res %>%
  filter(block == 7) %>% 
  group_by(condition, risky_choice) %>%
  summarise(
    n = length(cp),
    mean = mean(cp),
    sd = sd(cp),
    median = median(cp),
    IQR = IQR(cp)
    )

kable(s, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial") %>%
  column_spec(c(4, 6), bold = T)
```

<br>

</details>

<!-- One-Way ANOVA on Difference (High - Low) -->

<details>
  <summary>
  One-Way ANOVA on Difference (High - Low)
  </summary>
  
```{r}
source('r-scripts/choice-trials/pr_risky_diff_aov.R')
```

<h4> Main Effect </h4>

```{r}
kable(anova_diff, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

```{r}
f_vals <- round(anova_diff$`F-value`, 2)
p_vals <- ifelse(anova_diff$`p-value` < 0.001, 
                 '< 0.001', round(anova_diff$`p-value`, 3))
R2_vals <- round(anova_diff$pseudo_R2, 2)
```

**Effect of Condition:**

$F(`r anova_diff[2, 1]`, `r anova_diff[3, 1]`) = `r f_vals[2]`, p = `r p_vals[2]`, R^2_N = `r R2_vals[2]`$

<br>

<h4> Planned Contrasts </h4>

```{r}
kable(pc_diff, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

```{r}
b_vals <- round(pc_diff$Value, 2)
t_stat <- round(pc_diff$`t-value`, 2)
df_vals <- pc_diff$DF
p_vals <- ifelse(pc_diff$`p-value` < 0.001, 
                 '< 0.001', round(pc_diff$`p-value`, 3))
r_vals <- round(pc_diff$r_effect, 3)
```

**No Extreme vs. Extreme First:**

$b = `r b_vals[2]`, t(`r df_vals[2]`) = `r t_stat[2]`, p = `r p_vals[2]`, r = `r r_vals[2]`$

**Extreme Last vs. Extreme First:**

$b = `r b_vals[3]`, t(`r df_vals[3]`) = `r t_stat[3]`, p = `r p_vals[3]`, r = `r r_vals[3]`$

- Note: p-values for these two planned contrasts reflect a one-sided hypothesis test as per the pre-registered hypotheses. i.e., (G1 < G2) & (G1 < G3). The Welch t-test below tests whether G2 = G3.

<br>

<h4> Welch Two-Sided T-test </h4>

```{r}
t_stat <- round(welch_NE_v_E2$statistic, 2)
df <- round(welch_NE_v_E2$parameter, 2)
p_val <- round(welch_NE_v_E2$p.value, 3)
d_val <- round(d_NE_v_E2$estimate, 2)
```

**No Extreme vs. Extreme Last:**

$t(`r df`) = `r t_stat`$, $p = `r p_val`$, $d = `r d_val`$

<br>

</details>


<!-- One-Way ANOVA on High Value Choices-->

<details>
  <summary>
  One-Way ANOVA on High Value Choices
  </summary>
  
```{r}
source('r-scripts/choice-trials/pr_risky_high_aov.R')
```

<h4> Main Effect </h4>

```{r}
kable(anova_hv, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

```{r}
f_vals <- round(anova_hv$`F-value`, 2)
p_vals <- ifelse(anova_hv$`p-value` < 0.001, 
                 '< 0.001', round(anova_hv$`p-value`, 3))
R2_vals <- round(anova_hv$pseudo_R2, 3)
```

**Effect of Condition:**

$F(`r anova_hv[2, 1]`, `r anova_hv[3, 1]`) = `r f_vals[2]`, p = `r p_vals[2]`, R^2_N = `r R2_vals[2]`$

<br>

<h4> Planned Contrasts </h4>

```{r}
kable(pc_hv, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

```{r}
b_vals <- round(pc_hv$Value, 3)
t_stat <- round(pc_hv$`t-value`, 2)
df_vals <- pc_hv$DF
p_vals <- ifelse(pc_hv$`p-value` < 0.001, 
                 '< 0.001', round(pc_hv$`p-value`, 3))
r_vals <- round(pc_hv$r_effect, 3)
```

**No Extreme vs. Extreme First:**

$b = `r b_vals[2]`, t(`r df_vals[2]`) = `r t_stat[2]`, p = `r p_vals[2]`, r = `r r_vals[2]`$

**Extreme Last vs. Extreme First:**

$b = `r b_vals[3]`, t(`r df_vals[3]`) = `r t_stat[3]`, p = `r p_vals[3]`, r = `r r_vals[3]`$

- Note: These are two-sided tests.

<br>

<h4> Welch Two-Sided T-test </h4>

```{r}
t_stat <- round(welch_NE_v_E2$statistic, 2)
df <- round(welch_NE_v_E2$parameter, 2)
p_val <- round(welch_NE_v_E2$p.value, 3)
d_val <- round(d_NE_v_E2$estimate, 2)
```

**No Extreme vs. Extreme Last:**

$t(`r df`) = `r t_stat`$, $p = `r p_val`$, $d = `r d_val`$

<br>

</details>



<!-- One-Way ANOVA on Low Value Choices-->

<details>
  <summary>
  One-Way ANOVA on Low Value Choices
  </summary>
  
```{r}
source('r-scripts/choice-trials/pr_risky_low_aov.R')
```

<h4> Main Effect </h4>

```{r}
kable(anova_lv, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

```{r}
f_vals <- round(anova_lv$`F-value`, 2)
p_vals <- ifelse(anova_lv$`p-value` < 0.001, 
                 '< 0.001', round(anova_lv$`p-value`, 3))
R2_vals <- round(anova_lv$pseudo_R2, 2)
```

**Effect of Condition:**

$F(`r anova_lv[2, 1]`, `r anova_lv[3, 1]`) = `r f_vals[2]`, p = `r p_vals[2]`, R^2_N = `r R2_vals[2]`$

<br>

<h4> Planned Contrasts </h4>

```{r}
kable(pc_lv, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

```{r}
b_vals <- round(pc_lv$Value, 2)
t_stat <- round(pc_lv$`t-value`, 2)
df_vals <- pc_lv$DF
p_vals <- ifelse(pc_lv$`p-value` < 0.001, 
                 '< 0.001', round(pc_lv$`p-value`, 3))
r_vals <- round(pc_lv$r_effect, 3)
```

**No Extreme vs. Extreme First:**

$b = `r b_vals[2]`, t(`r df_vals[2]`) = `r t_stat[2]`, p = `r p_vals[2]`, r = `r r_vals[2]`$

**Extreme Last vs. Extreme First:**

$b = `r b_vals[3]`, t(`r df_vals[3]`) = `r t_stat[3]`, p = `r p_vals[3]`, r = `r r_vals[3]`$

- Note: These are two-sided tests.

<br>

<h4> Welch Two-Sided T-test </h4>

```{r}
t_stat <- round(welch_NE_v_E2$statistic, 2)
df <- round(welch_NE_v_E2$parameter, 2)
p_val <- round(welch_NE_v_E2$p.value, 3)
d_val <- round(d_NE_v_E2$estimate, 2)
```

**No Extreme vs. Extreme Last:**

$t(`r df`) = `r t_stat`$, $p = `r p_val`$, $d = `r d_val`$

<br>

</details>

<!-- Notes -->

<details>
  <summary>
  Notes
  </summary>

-  NE = No Extreme; E1 = Extreme First; E2 = Extreme Last

- ANOVAs were run using generalized least-squares fit by maximum likelihood.

- $R^2_N$ is Nagelkerke's (also known as Cragg and Uhler's) pseudo $R^2$ [@Nagelkerke]. It isn't interpreted in exactly the same way as a $R^2$ based on ordinary least-squares regression, but it is bounded by 0 and 1 and higher values indicate a better model fit.

</details>


